\addsec{Appendix}

\section{Publication notice}

This document was created as part of a project for the distance learning program in computer science at Trier University of Applied Sciences.
It documents the first milestone of the \textit{helios} project, a C++-based framework prototype for developing a \textit{Geometry Wars}-like game.


\subsection*{Copyright \& License}
\textcopyright 2025 Thorsten Suckow-Homberg, ORCID: \url{https://orcid.org/0009-0002-3389-8606}\\
This work is licensed under a Creative Commons Attribution 4.0 International License (CC BY 4.0).
The full license is available at \url{https://creativecommons.org/licenses/by/4.0/}.


\subsection*{Note on brand names}\\
\textit{Geometry Wars} is a registered trademark of Activision Publishing, Inc.
All other trademarks and product names mentioned in this document are the property of their respective owners.
The project described in this report is an independent, non-commercial academic prototype and is inspired by the original \textit{Geometry Wars} game.
The project is not affiliated with, endorsed by, or associated with Activision Publishing, Inc. in any way.


\subsection*{Suggested citation (Bib\TeX)}
\begingroup\small
\begin{verbatim}
@techreport{SuckowHomberg2025HeliosTR,
  author      = {Suckow-Homberg, Thorsten},
  title       = {helios: Design and prototypical implementation of a C++ game framework},
  institution = {Trier University of Applied Sciences, Department of Computer Science},
  type        = {Technical Report},
  year        = {2025},
  month       = {Nov},
  version     = {1.0},
  doi         = {10.5281/zenodo.xxxxxxx}
}
\end{verbatim}
\endgroup